Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\section{Method}

@@

\subsubsection{Cross Attention}
One of the key factors in target speaker extraction is to 
inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module, and it has 
achieved superior performance compared to other methods. Therefore, we apply 
the cross attention module to inject the reference embedding into the mixture. The details 
are in Fig.\ref{cross_attention}.
The cross attention module consists of a positional 
embedding layer, a cross-multiple head attention module, 
and a FiLM module. 
We use \(E_m\) as query and \(E_r\) as key and value for 
the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
is passed together with \(E_m\) to the feature-wise linear modulation (FiLM) get the final output of the module. The output of 
FiLM is denoted as \(E_f = FiLM(E_m, E_{spk}) = \gamma E_{spk} \cdot E_m  + \beta E_{spk} \) where 
\(\gamma\) and \(\beta\) are learnable parameters denoting the scaling and shifting vectors 
respectively. The output is then fed to the language model for later modeling.  
\subsubsection{Language Modeling}
We use encoder-only language models containing multiple self-attention modules to model the injected 
embedding \(E_f\). Due to encoder-only style, the LM is able to learn from all the positions. 
Finally, 6 linear classifiers each with dimension \(K\) is used to produce the probability 
distribution of each layer respectively.
Cross-entropy loss is applied between 
the output tokens and the clean tokens through discretizing the 
ground truth clean audio . 
\subsection{Decoding}

>>>>

\section{Method}
Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
pretrained models freezed during training. For the encoding stage, we use multiple layers of WavLM 
and publicly available Kmeans 
models in \cite{dasb} to produce the discretized tokens. We use a special concatenation 
strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
\cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
distribution of the clean tokens.

@@

\subsubsection{Cross Attention}
One of the key factors in target speaker extraction is to 
inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module, and it has 
achieved superior performance compared to other methods. Therefore, we apply 
the cross attention module to inject the reference embedding into the mixture. The details 
are in Fig.\ref{cross_attention}.
The cross attention module consists of a positional 
embedding layer, a cross-multiple head attention module, 
and a FiLM module. 
We use \(E_m\) as query and \(E_r\) as key and value for 
the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
is passed together with \(E_m\) to the feature-wise linear modulation (FiLM) get the final output of the module. The output of 
FiLM is denoted as \(E_f = FiLM(E_m, E_{spk}) = \gamma E_{spk} \cdot E_m  + \beta E_{spk} \) where 
\(\gamma\) and \(\beta\) are learnable parameters denoting the scaling and shifting vectors 
respectively. The output is then fed to the language model for later modeling.  
\subsubsection{Language Modeling}
We use encoder-only language models containing multiple self-attention modules to model the injected 
embedding \(E_f\). Due to encoder-only style, the LM is able to learn from all the positions. 
Finally, 6 linear classifiers each with dimension \(K\) is used to produce the probability 
distribution of each layer respectively.
Cross-entropy loss is applied between 
the output tokens and the clean tokens through discretizing the 
ground truth clean audio .
